\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{lmodern}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\setlength{\footskip}{5pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingNoDate}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% resume contents

\begin{document}
\begin{center}
  \textbf{\Huge \scshape Piotr Rybiec} \\ \vspace{1pt}
  \small +48 573 998 408 $|$ \href{mailto:piotrrybiec28@gmail.com}{\underline{piotrrybiec28@gmail.com}} $|$
  \href{https://linkedin.com/in/piotrek-rybiec}{\underline{linkedin.com/in/piotrek-rybiec}} $|$
  \href{https://github.com/a1eaiactaest}{\underline{github.com/a1eaiactaest}} $|$
\end{center}

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Co-founder}{August 2022 -- Present}
      {QuasiPhi Project}{Warsaw, Poland}
      \resumeItemListStart
        \resumeItem{Co-founded and developed a machine learning startup that focuses on analysing time series data for patterns.}
        \resumeItem{Created efficient micro-service solution for fetching and storing time-series financial data from various exchanges in Go, PostgreSQL and TimescaleDB.}
        \resumeItem{Implemented proprietary algorithms that were a major distinguishing factor of the product, while experimenting on Transformer architecture.}
      \resumeItemListEnd
    \resumeSubheading
      {Java Summer Intern}{July 2024 -- September 2024}
      {eService Sp. z o.o.}{Warsaw, Poland}
      \resumeItemListStart
        \resumeItem{Developed internal data-intensive REST APIs and data pipelines utilizing Java 17, Hibernate, Spring Framework and it's derviatives.}
        \resumeItem{Designed and developed full-stack applications in Node.js, React.js and Tailwind CSS.}
        \resumeItem{Assesed and troubleshot issues arising from the diversity of many different coding environments.}
      \resumeItemListEnd
    \resumeSubheading
      {Full-stack Software Engineer}{June 2023 -- August 2023}
      {Dopamine\&Co}{Warsaw, Poland}
      \resumeItemListStart
        \resumeItem{Developed a MVP for a full-stack web application, focusing on addressing fundamental user needs and providing sufficient market validation.}
        \resumeItem{Optimized the application for scalability and applied authentication and authorization mechanisms.}
        \resumeItem{Implemented a REST API in Django and used React.js for the frontend.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheadingNoDate
      {Go Chess Engine}{January 2025}
      \resumeItemListStart
        \resumeItem{Implemented a chess engine based on minimax alpha-beta pruning search algorithm.}
        \resumeItem{Created a frontend allowing user to play with the computer in a comfortable way.}
      \resumeItemListEnd
    \resumeSubheading
      {RERE}{September 2021 -- May 2022}
      {Bednarska Real Highschool}{Warsaw, Poland}
      \resumeItemListStart
        \resumeItem{Led the developement of a master-slave infrastructure for a distributed system of hardware radio stations communicating with a mother station.}
        \resumeItem{Implemented Arduino and Adafruit Feather controllers communicating with a Raspberry Pi via radio-serial pipeline.}
        \resumeItem{Optimized the data flow for transparent and efficient communication for over 20 stations.}
        \resumeItem{Implemented a Python middleware for data processing and database communication.}
        \resumeItem{Created a online dashboard allowing for real-time monitoring of every station.}
      \resumeItemListEnd
    \resumeSubheading
      {Voluntary work}{2022 -- 2023}
      {Marek Kaminski Foundation}{Poland}
      \resumeItemListStart
        \resumeItem{Took an active part in an initiative called 'Marsze Mocy', dedicated to raising awareness about the importance of mental health across the youth.}
        \resumeItem{As a team, raised over 400,000 PLN to found a preventive-motivational LifePlan Academy courses.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Education}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Polish-Japanese Academy of Information Technology}{Warsaw, Poland}
        {Bachelor of Science in Computer Science}{2024 -- 2027}
      \resumeSubheading
        {Bednarska Real High School}{Warsaw, Poland}
        {Computer Science Specialized Track, Mathematics and Physics Major}{2020 -- 2024}
  \resumeSubHeadingListEnd


\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: Java, Python, Go, JavaScript, SQL, C, C++, Bash} \\
      \textbf{Frameworks}{: Spring, Hibernate, Django, React.js, Node.js, PyTorch, TensorFlow, MLX, Tailwind CSS} \\
      \textbf{Tools}{: Git, Linux, Docker, GCP, debuggers and decompilers} \\
      \textbf{Libraries}{: NumPy, Pandas, Matplotlib, Seaborn} \\
    }}
  \end{itemize}

  \end{document}

